\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\markboth{ACKNOWLEDGEMENTS}{ACKNOWLEDGEMENTS}

\section*{Chapter 1}
We thank Jana Hörsch, Laila Darouich, Alex Bruttel, Daniel Zuñiga and the animal caretaker team at the Max Planck Institute for Ornithology in Radolfzell for assistance with data collection and monitoring animal health each day. We thank Iain Couzin, Andrew Straw and two anonymous reviewers for helpful comments on the manuscript. We also thank Iain Couzin for his support of the project. This work was funded by the Max Planck Society. D.R.F. and A.A.M.‐C. received additional funding from the German Research Foundation (DFG grant FA 1420/4‐1 awarded to D.R.F.).

\section*{Chapter 2}
We are indebted to Talmo Pereira et al. and A. Mathis et al. for making their software open-source and freely-available---this project would not have been possible without them. We also thank M. Mathis and A. Mathis for their comments, which greatly improved the manuscript. We thank Fran\c{c}ois Chollet, the Keras and TensorFlow teams, and Alexander Jung for their open source contributions, which provided the core programming interface for our work. We thank A. Strandburg-Peshkin, Vivek H. Sridhar, Michael L. Smith, and Joseph B. Bak-Coleman for their helpful discussions on the project and comments on the manuscript. We also thank M.L.S. for the use of his GPU. We thank Felicitas Oehler for annotating the zebra posture data and Chiara Hirschkorn for assistance with filming the locusts and annotating the locust posture data. We thank Alex Bruttel, Christine Bauer, Jayme Weglarski, Dominique Leo, Markus Miller and loobio GmbH for providing technical support. We acknowledge the NVIDIA Corporation for their generous donations to our research. This project received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No. 748549. B.R.C. acknowledges support from the University of Konstanz Zukunftskolleg's Investment Grant program. I.D.C. acknowledges support from NSF Grant IOS-1355061, Office of Naval Research Grants N00014-09-1-1074 and N00014-14-1-0635, Army Research Office Grants W911NG-11-1-0385 and W911NF14-1-0431, the Struktur-und Innovationsfonds fur die Forschung of the State of Baden-W\"urttemberg, the DFG Centre of Excellence 2117 “Centre for the Advanced Study of Collective Behaviour" (ID: 422037984), and the Max Planck Society.

\section*{Chapter 3}
We thank Gordon Berman and members of the Berman lab, Tim Landgraf, Ben Wild, David Dormagen, Conor Heins, Blair Costelloe, Ian Etheredge, and Ari Strandburg-Peshkin for their helpful comments on the manuscript. We are also grateful to Mike Costelloe for his creative advice on the figures, Einat Couzin-Fuchs and Dan Bath for their expert input, and Michael Smith for the use of his GPU. J.M.G. and I.D.C. acknowledge support from the Deutsche Forschungsgemeinschaft
(DFG, German Research Foundation) under Germany’s Excellence Strategy - EXC 2117 - 422037984. I.D.C. acknowledges support from NSF Grant IOS-1355061, Office of Naval Research Grant (ONR, N00014-19-1-2556), the Struktur-und Innovationsfonds f\"ur die Forschung of the State of Baden-W\"urttemberg, and the Max Planck Society.
